%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,hidelinks]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Adam J. Gray -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Unit A 8/F 58-62 Caine Rd\\ % Address line 1
\> Mid-Levels, Hong Kong \\ % Address line 2
{\bf Date of Birth} \> 23$^{rd}$ May 1991 \\ % Date of birth
{\bf Nationality} \> Australian  % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf LinkedIn } \> \href{https://hk.linkedin.com/in/adam-gray-56852364}{linkedin.com/in/adam-gray-56852364} \\ % Mobile phone
{\bf GitHub } \> \href{https://github.com/adamjoshuagray}{github.com/adamjoshuagray} \\
{\bf Mobile Phone} \> +852 6079 5613 \\ % Mobile phone
{\bf Email} \> \href{mailto:adam.joshua.gray@gmail.com}{adam.joshua.gray@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

Adam has worked extensively in algorithmic trading over a number of years. He has both buy-side and sell-side
experience and a strong understanding of market microstructure. Adam is a motivated and energetic individual who
is constantly looking to learn more and develop his skills. Adam is looking for a role where he can use his skills
to have a direct impact on PnL.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education / Awards}

\tabbedblock{
\bf{2010-2014} \> BSc in Advanced Mathematics - University of New South Wales, Australia \\[5pt]
\>\+
\textit{First Class Honors in Fractional Calculus}
}

%------------------------------------------------

\tabbedblock{
\bf{2014} \> The Buchwald Award\\[5pt]
\>\+
\textit{For the best performance leading to Honors Year in Applied Mathematics at UNSW.}
}

%------------------------------------------------

\tabbedblock{
\bf{2013} \> Summer Research Scholar\\[5pt]
\>\+
\textit{Markov Chain Monte Carlo techniques applied to graph mixing problems.}
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Jan 2015 -}{Present}
{Goldman Sachs, 65F Cheung Kong Center, Hong Kong}
{http://www.gs.com}
{Analyst - Fixed Income Algo and Quant Strat}
{

Worked on the roll out of market making and order management infrastructure. \\
Co-developed a market simulation framework (L3 market data replay) for accurate simulation
of trading and execution strategies.\\
Developed basic a Gaussian risk model to improve performance of quoting strategies in simulation. \\
Developed a genetic algorithm optimization system for trading system parameters. \\
Investigated estimating order action (cancelation / trade) probabilities using machine learning techniques
such as logistic regression and support vector machines.
This work requires extensive use of C++ and Python (ipyparallel for distributed computing).\\


\textbf{Technologies:} Python (2.7), C++, Java, numpy, scipy, sklearn, pandas, Slang (in-house), Excel, svn, cvs, git
}
%------------------------------------------------

\job
{Nov 2013 -}{Feb 2014}
{Goldman Sachs, 47F governor Phillip Tower, Sydney}
{http://www.gs.com}
{Summer Intern}
{
Worked on transaction cost analysis reporting for agency equity algos (VWAP, TWAP, IS, etc).\\
Developed market knowledge of the Australian equities market and the use of algos in equities markets in general. \\

\textbf{Technologies:} Slang (in-house), Excel
}


%------------------------------------------------

\job
{Jan 2010 -}{Aug 2011}
{eStats Capital, Sydney}
{http://www.bloomberg.com/research/stocks/private/snapshot.asp?privcapId=139377089}
{Software Developer - Part Time and Full Time}
{

Developed monitoring and automation software in C\# and built trading and rules execution
infrastructure in C++. Worked extensively with Object Trading's Front Runner API for market connectivity.\\
\textbf{Technologies:} C\#, C++, boost, FrontRunner API (market connectivity), MySQL

}


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\skillgroup{Programming Languages / Technologies}
{
\textit{Python 2.7:} numpy, sklearn, pandas, scipy\\
\textit{C\#}\\
\textit{C++ (11):} boost\\
\textit{Java} \\
\textit{Google Protocol Buffers}\\
\textit{MySQL}\\
\LaTeX \\
\textit{Octave / Matlab}

}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
\interest{Programming / Mathematics}
\interest{Bike Riding}
\interest{Photography}
}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Bernard Orenstein \\ % Referee name
{\bf Company} \> eStats Capital. \\ % Referee company
{\bf Position} \> Managing Director \\ % Referee job title
{\bf Contact} \> \href{mailto:berniespots@gmail.com}{berniespots@gmail.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Dr Chris Tisdell\\ % Referee name
{\bf Organization} \> University of New South Wales \\ % Referee company
{\bf Relationship} \> Honors Supervisor \\ % Referee job title
{\bf Contact} \> \href{mailto:cct@unsw.edu.au}{cct@unsw.edu.au} % Referee contact information
\end{tabbing}}

%----------------------------------------------------------------------------------------

\end{document}
